---
title: "Luxury Effect Remix"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Goal

A couple years ago, some collaborators and I published a pretty cool paper that found a luxury effect for arthropod diversity in homes. In short, houses in wealthier neighborhoods had more kinds of bugs in their homes. Here's the open access paper from [Biology Letters](http://rsbl.royalsocietypublishing.org/content/12/8/20160322).

Through working on that paper I learned about the rich trove of U.S. census data. It seemed like a good exercise to revisit the script I wrote at the time to see how I can improve it and make it more usable for other people.

My general plan of attack is to first use the data I made available in the supplementary files section of the original paper and dubplicate the analyese in a more reproducible format.  Then, I'm going to go a step back and reaccess the census data with the original uncleaned dataset to create a clean pipeline. Throughout the process, I'm going to also look for ways to improve on the original paper.

## Original Analyses

The following files were included in the original paper.
```{r firstThingsFirst}
# load libraries
library(tidyverse)
library(vegan)
library(ggmap)
library(ggrepel)
library(ggpubr)
library(stringr)
library(acs)

# load files
load('data/aoh.Rdata')
load('data/houses.Rdata')
```

## Basic EDA

First let's take a look at what's in each of the files

```{r initialLookAOH, echo=FALSE}
head(aoh)
summary(aoh)
```

The main 'aoh' file is organized in a way such that each row is a unique arthropod family (such as Formicidae for ants or Cecidomyiidae for gall mideges) in each unique collecting event (each room in each house, such as the basement of house 23 or the 3rd bedroom in house 38). For each row there can be multiple morphospecies per family (in our case, anywhere from 1-20).

```{r initialLookHOUSES}
head(houses)
summary(houses)
```

The 'houses' file gives information on each (surprise surprise) house.  Rooms (the unique collecting events) have been collapsed to just the house level, so a conservative estimate of the number of arthropod families is listed for each house (the assumption that if there are 3 morphospecies of a given arthrpod family in one room of a house, and 10 in another, all 3 of those prior species are redundant in the the 10 in the other room). The 'houses' file also has statistics about the characteristics of each house, such as how much and how diverse the ground cover and canopy cover on the property are, the size of the house, house value, and things going on at the neighborhood scale based on remote sensing and US census data.


# Make dataset more usable
For some reason, the 'houses' file does not have lat/lon data which we need for the spatial autocorrelation analysis, and for some reason also does not have a houseID column.  A way to get around that is to find one of the overlapping variables that is unique for each house and use that as the linking factor.

```{r linkData}
# It seems like 2 of the houses somehow share the same variables.
unique(aoh$Imp100m)

# This is better!
unique(aoh$Imp500m)

# Cross reference with 'houses' file. Perfect.
unique(houses$Imp500m)

# Collapse 'aoh' file to only contain unique values for each house 
aoh_collapsed <- aoh %>%
  select (houseID, Imp500m, lat, lon) %>%
  distinct()

# Now link the two
houses <- houses %>%
  left_join(aoh_collapsed, by = "Imp500m")

```

# Check for spatial autocorrelation 
This code works, but should check if there is now a better or alternative way to check for spatial autocorrelation.
```{r autocorrelation}
library(vegan)
library(RColorBrewer)
library(lme4)
library(ggplot2)
library(ade4)
#mantel tests for spatial autocorrelations
house.dists<-dist(cbind(houses$lon, houses$lat))
fam.dists<-dist(houses$numFam)
income.dists<-dist(houses$incomeAvg)
gc.dists<-dist(houses$groundCoverAvg)
gd.dists<-dist(houses$groundDivAvg)
imp.dists<-dist(houses$Imp500m)
mantel.rtest(house.dists, imp.dists, nrepet=999)
```



## Analyses
# Variable Selection
We considered several biological, geophysical and socioeconomic variables at local and landscape scales that we hypothesized could influence indoor arthropod diversity (table 1), and scaled them from 0 to 1. We then created a correlation matrix with these initial 12 variables with R package corrplot [15] (electronic supplementary material, figure S1). We found some variables to be highly correlated with one another (Pearson's r > |0.5|), so restricted our analyses to seven factors that maximized coverage and questions of interest. On the landscape scale, we included remotely sensed canopy cover within a 100 m radius, remotely sensed impervious surface area within a 500 m radius, and mean neighbourhood income at the census block level. On the scale of each property's extent, we included house age, local ground vegetation diversity, local ground vegetation cover and local canopy cover. We suspected house square footage of being linked with sampling effort, so included it in the model to account for potential bias. 

```{r corrplot}
#scaling variables from 0 to 1
range01 <- function(x){(x-min(x))/(max(x)-min(x))}
Imp100m<-range01(houses$Imp100m)
Can100m<-range01(houses$Can100m)
Imp500m<-range01(houses$Imp500m)
Can500m<-range01(houses$Can500m)
propRenter <-range01(houses$propRenter)
income<-range01(houses$incomeAvg)
houseAge<-range01(houses$houseAge)
totalValue <-range01(houses$totalValue)
canopyDiv<-range01(houses$canopyDivAvg)
groundDiv<-range01(houses$groundDivAvg)
groundCover<-range01(houses$groundCoverAvg)
canopyCover<-range01(houses$canopyCoverAvg)
veg<-range01(houses$vegAvg)
                       
aoh.scaled<-data.frame(numFam=houses$numFam, Imp100m, Can100m, Imp500m, Can500m, 
                       income, houseAge, totalValue, canopyDiv, groundDiv, groundCover,
                       canopyCover, veg, houses$sqFeet)

# correlation matrix (delete gcCat from above)
library(corrplot)
P <- cor(aoh.scaled, method="pearson")
K <- cor(aoh.scaled, method="kendall")
S <- cor(aoh.scaled, method="spearman")
corrplot(P, method = "number")
corrplot(S, method = "number")
corrplot(K, method = "number")

## plotting this shit
cloud(numFam~income+groundDiv, data=aoh.scaled)
plot(numFam~Imp500m, data=aoh.scaled)

```


# GLMs
We then used R package glmulti, which does automated model selection with generalized linear models (GLMs) [16], to generate GLMs of all possible model combinations with a Poisson distribution (with house arthropod diversity as the response variable and the explanatory variables listed above) and automatically select the best model based on Akaike information criterion (AIC) and Bayes information criterion (BIC) scores. Then, with the most critical environmental variables identified, we tested for the effect of interactions among those that made biological sense.
```{r glmulti}
#copy and pasted in. need to also get rJava
# The super awesome glmulti
library(rJava)
library(glmulti)
mALL<-glmulti(numFam~Can100m+Imp500m+houseAge+income+groundDiv+groundCover
            +canopyCover+sqFeet, 
           data=aoh.scaled, family="poisson", method="h", level=1, crit="aic")
mRARE<-glmulti(numRARE~Can100m+Imp500m+houseAge+income+groundDiv+groundCover+canopyCover+sqFeet, 
           data=aoh.scaled, family="poisson", method="h", level=1, crit="aic")
m<-glmulti(propRARE~Can100m+Imp500m+houseAge+income+groundDiv+groundCover+canopyCover+sqFeet, 
           data=aoh.scaled, family="binomial", method="h", level=1, crit="aic")
m<-glmulti((propRAREscaled*100)~Can100m+Imp500m+houseAge+income+groundDiv+groundCover+canopyCover+sqFeet, 
           data=aoh.scaled, family="poisson", method="h", level=1, crit="aic")
mInterior<-glmulti(numFam~income+Imp500m+groundDiv+groundCover+clutter+plant+cat+dog+pesticide+sqFeet, 
              data=aoh.scaled, family="poisson", method="h", level=1, crit="aic")
summary(mALL)
summary(mRARE)
summary(mInterior)
plot(mInterior, type="s")
plot(mInterior, type="w")
plot(m, type="s")

coef(mInterior, select="all", varweighting="Buckland", icmethod="Lukacs", alphaIC=0.05)
 

```
 Interaction
```{r}
m<-glm(numFam~income+groundDiv+groundCover+income*groundCover+
         sqFeet, 
        data=aoh.scaled, family="poisson")
m1<-glm(numFam~income+Imp500m+groundDiv+groundCover+cat+dog+sqFeet, 
         data=aoh.scaled, family="poisson")
summary(m)
summary(m1)

m2<-glm(numFam~Imp500m+income+groundCover+groundDiv+income*groundCover+sqFeet, 
        data=aoh.scaled, family="poisson")
summary(m2)## Groundcover and income have a strong interaction!  Let's plot that.
m3<-glm(numFam~Imp500m+income+groundCover+groundDiv+cat+dog+income*groundCover+sqFeet, 
        data=aoh.scaled, family="poisson")
summary(m3)
m3<-glm(numFam~Imp500m+income+groundCover+groundDiv+cat+dog+sqFeet, 
        data=aoh.scaled, family="poisson")
summary(m3)


```
 
 
 
 ## PLOTS
 Interaction plot
```{r interaction}
# PLOTTING
aoh.scaled$gcCat<-factor(aoh.scaled$gcCat, levels=c("Low", "Med", "High"))
c<-ggplot(aoh.scaled, aes(y=numFam, x=income, colour=gcCat))
c+ stat_smooth(method=lm, se=FALSE)+geom_point()+scale_x_continuous(labels=scales::dollar)+
  labs(y="Number of arthropod families", x="Average neighborhood income", colour="Ground cover")+
  theme_bw(base_size=30)
  
```
 
